### 2019-11-10 thesis/txt/4-tool.tex
finish updating techniques section, write implementation section

\chapter{Tool Implementation}
\label{sec:implementation}
We implemented prototypes for our three focus information retrieval techniques to evaluate them on our collected build logs.
This section will present our unified interface and describe the implementation of each of the techniques.

@@

%\section{Common Interface}
\begin{lstlisting}
Usage: ruby run-extraction.rb -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>
       ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>
       ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>
       ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>

Specific options:
    -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
    -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
    -e, --example-set EXAMPLE_SET    The filename of the example set to use
    -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
    -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
    -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
    -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
    -v, --verbose                    Print additional interesting output apart from only the retrieval output
    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
    -r, --regex REGEX                Regex to match on build log file content in regex based retrieval

Common options:
    -h, --help                       Show this message
\end{lstlisting}
As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces. Our unified interface then in turn calls the various different IE techniques over the command line.

We provide two different modes: \emph{analysis} and \emph{evaluation}.
The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output. The \emph{evaluation} takes an

unification tool, reference CLI somehow nicely?,

ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)

%\section{Overall Implementation Remarks}
There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}

\subsection*{Preprocessing Log Text}
\label{sec:impl-preprocessing}

%\section*{PBE}
\label{sec:impl-pbe}
The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
implementation details :)

C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

%\section*{IR Similarity}
\label{sec:impl-ts}
impl details,

R, text2vec, tokenized vectors, impl of preprocessing?

don't repeat from IE models section!

%\section*{Keyword search}
\label{sec:impl-skws}
impl details,

R, simple!

>>>>

\chapter{Tool Implementation}
\label{sec:implementation}
To evaluate PBE, CTS and KWS on the \emph{Failing Build Log Data Set} we implemented them and a unifying interface to retrieve chunks from build logs.

@@

%\section{Common Interface}
% \begin{lstlisting}
% Usage: ruby run-extraction.rb
%             -a analyze -t <technique: ir, pbe, random> -e <example_set> -p <path_to_file_to_analyze>
%        ruby run-extraction.rb -a evaluate -t <technique: ir, pbe, keyword, random> -e <example_set> -s <selection_technique> -l <step_count_for_learning> -c <test_count>
%        ruby run-extraction.rb -a analyze -t keyword -k <keyword, keyword, ...> -p <path_to_file_to_analyze>
%        ruby run-extraction.rb -a analyze -t regex -r <regex to match extraction> -p <path_to_file_to_analyze>

% Specific options:
%     -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
%     -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
%     -e, --example-set EXAMPLE_SET    The filename of the example set to use
%     -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
%     -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
%     -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
%     -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
%     -v, --verbose                    Print additional interesting output apart from only the retrieval output
%     -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
%     -r, --regex REGEX                Regex to match on build log file content in regex based retrieval

% Common options:
%     -h, --help                       Show this message
% \end{lstlisting}

The unified interface is implemented in Ruby and gives access to all the CTRs we implemented.
This section describes how to use it to retrieve chunks for a build log or evaluate a CRT.
% As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interface. Our unified interface then in turn calls the various different IE techniques over the command line.

To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:todo} for the definition of an example set.
    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
\end{itemize}

To evaluate a CTR use the option \textttt{-a evaluate} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:todo} for the definition of an example set.
    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
    Manual selects the examples according to the sequence defined in the example set file.
    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
    Currently only \texttt{1} is supported.
\end{itemize}

The unification tool calls the separate chunk retrieval implementations over the command line.
Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
We implemented the CTS chunk retrieval using R and the text2vec~\cite{text2vec2019webpage} library.
KWS and RLR are implemented with R.

% We provide two different modes: \emph{analysis} and \emph{evaluation}.
% The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output. The \emph{evaluation} takes an

% unification tool, reference CLI somehow nicely?,

% ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)

%\section{Overall Implementation Remarks}
% There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
% The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}

% \subsection*{Preprocessing Log Text}
% \label{sec:impl-preprocessing}

%\section*{PBE}
% \paragraph{Program Synthesis by Example (PBE)}
% \label{sec:impl-pbe}
% Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
% % The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
% % implementation details :)

% % C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

% \paragraph{Common Text Similarity (CTS)}
% \label{sec:impl-ts}
% We implemented the CTS chunk retrieval using R and the text2vec library.

% % impl details,

% % R, text2vec, tokenized vectors, impl of preprocessing?

% % don't repeat from IE models section!

% \paragraph{Keyword Search (KWs)}
% \label{sec:impl-skws}
% impl details,

% R, simple!
